### 2017-01-16 text/Chapter02.tex
Edits pages 0-30

Variable access represents a form of context-dependence. For example, an expression $x+y$ can be
only evaluated if the environment provides values for variables $x$ and $y$. A variable
\emph{requirements} can be satisfied in two standard ways that are characterized as \emph{dynamic}
and \emph{static} (or lexical) variable binding. Consider the following simple program:
%
\begin{equation*}
\begin{array}{l}
\kvd{let}~\ident{f}=\\[-0.25em]
\qquad\kvd{let}~\ident{x}=10~\kvd{in}\\[-0.25em]
\qquad\lambda \ident{y}\rightarrow \ident{x}+\ident{y}~\kvd{in}\\[-0.25em]
\kvd{let}~\ident{x}=5~\kvd{in}\\
\ident{f}~0
\end{array}
\end{equation*}
%
The program can be evaluated in two ways, depending on the variable binding mechanism:
%
\begin{itemize}
\item \textsc{Static (lexical) binding.} In a language with static binding (such as ML or Java),
  the variable \ident{x} inside the body of the lambda function is statically bound to the
  declaration in the lexical scope -- that is, the variable on the second line -- and the
  expression evaluates to 10.

\item \textsc{Dynamic binding.} In a language with dynamic binding (some variants of LISP), the
  variable value is dynamically bound to the last value that has been added to the environment
  during program execution. Thus, the \ident{x} variable inside the lambda function refers to
  \ident{x} defined on line 5 of the sample and the expression evaluates to 5.
\end{itemize}

@@

In static and dynamic scoping, all variable requirements are always placed on one site. However,
those are not the only two options. It is conceivable that a language would use a mechanism that
splits variable requirements differently and combines aspects of dynamic and static binding. For
example, the language could use static binding by default, but resort to dynamic binding if a
variable is not available in the lexical scope. One such system is Haskell's implicit parameters
discussed in the next section.

Languages with static scoping resolve variable bindings at compile-time. In contrast,
languages with dynamic variable binding typically do not perform compile-time checks -- if a
program attempts to access a variable that is not available in the environment, a runtime error
occurs. This is possibly an artifact of their implementation -- implementing static binding
\emph{without} checking would be cumbersome and implementing static checking for dynamic binding is
requires a more sophisticated type system than traditional (Section~\ref{sec:path-effects-coeff}).

@@

Haskell uses static binding for ordinary variables, but it additionally provides a feature named
\emph{implicit parameters} \cite{app-implicit-parameters} that adds a special kind of variables,
written as \ident{?param}, which use a particular combination of static and dynamic binding.

@@

\paragraph{Thesis perspective.}
Just like the F\# function in the above example, certain expressions in context-aware languages
developed in this thesis have multiple valid typing derivations and their semantics depends on the
type. In F\#, the compiler determines a unique typing derivation based on other parts of the program
(if type is not uniquely determined, it either chooses a default or fails). In our languages, we
also determine a unique typing derivation. However, rather than relying on type information from
other parts of the program, we explicitly define an algorithm that chooses the preferred unique
derivation (Section~Section~\ref{sec:flat-unique} and Section~\ref{sec:struct-unique}).

This approach decouples two important aspects of context-aware programming and lets us study them
independently -- the semantics of context-aware programs and the domain-specific way of resolving
ambiguities in how context demands are satisfied. In our treatment of implicit parameters, we consider
multiple typing derivations (representing a range with static and dynamic scoping at opposite ends),
but we uniquely choose one preferred typing (in case of implicit parameters, mimicking the
behaviour of Haskell).

@@

Type and effect systems are usually specified as judgements of the form $\Gamma \vdash e : \tau, \cclrd{r}$,
meaning that the expression $e$ has a type $\tau$ in a (free-variable) context $\Gamma$ and
additionally may have effects described by $\cclrd{r}$. Effect systems are typically added to a
language that already supports effectful operations as a way of increasing the safety -- the type
and effect system provides stronger guarantees than a plain type system. Filinsky
\cite{effects-comprehensive} refers to this approach as \emph{descriptive}\footnote{In contrast
to \emph{prescriptive} effect systems that implement computational effects in a pure language
-- such as monads in Haskell.}.

@@

When using monads, we distinguish effect-free values $\tau$ from programs, or
computations $\mtyp{}{\tau}$. The \emph{monad} $\mtyp{}{}$ abstracts the \emph{notion of
computation} and provides a way of constructing and composing effectful computations:

~

\begin{definition}
A \emph{monad} over a category $\catc$ is a triple $(M, \ident{unit}, \ident{bind})$ where:
\begin{compactitem}
\item $M$ is a mapping on objects (types) $M : \catc \rightarrow \catc$
\item $\ident{unit}$ is a mapping $\alpha \rightarrow \mtyp{}{\alpha}$
\item $\ident{bind}$ is a mapping $(\alpha \rightarrow \mtyp{}{\beta})
  \rightarrow (\mtyp{}{\alpha} \rightarrow \mtyp{}{\beta})$
\end{compactitem}
such that, for all $f:\alpha \rightarrow \mtyp{}{\beta}$ and $g:\beta \rightarrow \mtyp{}{\gamma}$:
\begin{align}
\tag{\emph{left identity}}
  \ident{bind}~\ident{unit} &= \idf{}
  \\
\tag{\emph{right identity}}
  \ident{bind}~f \circ \ident{unit} &= f
  \\
\tag{\emph{associativity}}
  \ident{bind}~(\ident{bind}~g \circ f) &= (\ident{bind}~f) \circ (\ident{bind}~g)
\end{align}
\end{definition}

\noindent
Without providing much details, we note that well known examples of monads include the partiality
monad ($\mtyp{}{\alpha} = \alpha + {\bot}$) also corresponding to the \ident{Maybe} type in
Haskell, list monad ($\mtyp{}{\tau} = 1 + (\tau \times \mtyp{}{\tau})$) and other.
In programming language semantics, monads can be used in two distinct ways.

@@

\paragraph{Language semantics.} When using monads to provide semantics of a language, we do not
need to extend the language in any way -- we assume that the language already contains the
effectful primitives (such as the assignment operator $x \leftarrow e$ or other). A judgement
of the form $x\!:\!\tau_1 \vdash e : \tau_2$ is interpreted as a morphism $\tau_1 \rightarrow \mtyp{}{\tau_2}$,
meaning that any expression is interpreted as an effectful computation. The semantics of variable
access and the application of a primitive function $f$ is interpreted as follows:
%
\begin{equation*}
\begin{array}{rcl}
 \sem{x\!:\!\tau_1 \vdash x : \tau_1} &=& \ident{unit}_\mtyp{}{}\\
 \sem{x\!:\!\tau_1 \vdash f~e : \tau_3} &=& (\ident{bind}_\mtyp{}{}~f) \circ \sem{e}\\
\end{array}
\end{equation*}
%
Variable access is an effect-free computation, that returns the value of the variable, wrapped
using $\ident{unit}_\mtyp{}{}$. In the second rule, we assume that $e$ is an expression using
the variable $x$ and producing a value of type $\tau_2$ and that $f$ is a (primitive) function
$\tau_2 \rightarrow \mtyp{}{\tau_3}$. The semantics lifts the function $f$ using $\ident{bind}_\mtyp{}{}$
to a function $\mtyp{}{\tau_2} \rightarrow \mtyp{}{\tau_3}$ which is compatible with the
interpretation of the expression $e$.

@@

\paragraph{Meta-language interpretation.} ~When designing meta-language based on monads, we need to
extend the lambda calculus with additional type(s) and expressions that correspond to monadic
primitives:
%
\begin{align*}
\tau &:= \ident{num} \sep \tau_1 \rightarrow \tau_2 \sep \mtyp{}{\tau} \\
   e &:= x \sep f~e \sep \kvd{return}_\mtyp{}{}~e \sep \kvd{let}_\mtyp{}{}~x \Leftarrow e_1~\kvd{in}~e_2
\end{align*}
%
The types consist of the primitive type, function type and a type constructor that
represents monadic computations. Thus the expressions in the language can create both
effect-free values, such as $\tau$ and computations $\mtyp{}{\tau}$. The additional expression
$\kvd{return}_\mtyp{}{}$ is used to create a monadic computation (with no effects) from a
value and $\kvd{let}_\mtyp{}{}$ is sequences effectful computations. In the semantics,
monads are not needed to interpret variable access and application, they are only used in the
semantics of additional (monadic) constructs:
%
\begin{equation*}
\begin{array}{rcl}
\sem{x\!:\!\tau \vdash x : \tau} &=& \idf{}\\
\sem{x\!:\!\tau_1 \vdash f~e : \tau_3} &=& f \circ \sem{e}\\
\sem{x\!:\!\tau_1 \vdash \kvd{return}_\mtyp{}{}~e : \mtyp{}{\tau_2}} &=& \ident{unit}_\mtyp{}{} \circ \sem{e}\\
\sem{x\!:\!\tau_1 \vdash \kvd{let}_\mtyp{}{}~y \Leftarrow e_1~\kvd{in}~e_2 : \mtyp{}{\tau_3}} &=&
  \ident{bind}_\mtyp{}{}~\sem{e_2} \circ \sem{e_1}
\end{array}
\end{equation*}

@@

While Uustalu and Vene use comonads to define the \emph{language semantics} (the first style
of Moggi), Nanevski, Pfenning and Davies use comonads as part of meta-language, in the form
of $\square$ modality, to reason about context-dependent computations (the second style of
Moggi). Before looking at the details, we use the following definition of comonad:

~

\begin{definition}
A \emph{comonad} over a category $\catc$ is a triple $(C, \ident{counit}, \ident{cobind})$ where:
\begin{compactitem}
\item $C$ is a mapping on objects (types) $C : \catc \rightarrow \catc$
\item $\ident{counit}$ is a mapping $\ctyp{}{\alpha} \rightarrow \alpha$
\item $\ident{cobind}$ is a mapping $(\ctyp{}{\alpha} \rightarrow \beta)
  \rightarrow (\ctyp{}{\alpha} \rightarrow \ctyp{}{\beta})$
\end{compactitem}
%
such that, for all $f:\ctyp{}{\alpha} \rightarrow \beta$ and $g:\ctyp{}{\beta} \rightarrow \gamma$:

@@

\noindent
The definition is similar to a monad with ``reversed arrows''. Intuitively, the $\ident{counit}$
operation extracts a value $\alpha$ from a value that carries additional context $\ctyp{}{\alpha}$.
The $\ident{cobind}$ operation turns a context-dependent function
$\ctyp{}{\alpha} \rightarrow \beta$ into a function that takes a value with context, applies
the context-dependent function to value(s) in the context and then propagates the context. The
next section makes this intuitive definition more concrete. More detailed discussion about
comonads can be found in Orchard's PhD thesis \cite{comonads-dom-thesis}.

@@

In the outline presented here, we ignored lambda abstraction. Similarly to monadic semantics,
where lambda abstraction requires \emph{strong} monad, the comonadic semantics also requires
additional structure called \emph{symmetric (semi)monoidal} comonads. This structure is
responsible for the splitting of context-requirements in lambda abstraction. Note that this is
what happens in the unusual (\emph{abs}) rule in Figure~\ref{fig:path-coeff}, which distinguishes
coeffect systems from effect systems.

@@

In languages inspired by modal logics, types can have the form $\square \tau$. In the work of
Pfenning and Davies, this is the type of a term that is provable with no assumptions. In distributed
programming language ML5 by Murphy et al. \cite{app-distributed-ml5,logic-distributed-calculus}, the
$\square \tau$ type means \emph{mobile code}, that is code that can be evaluated at any node of a
distributed system (the evaluation corresponds to the axiom $\square \tau \rightarrow \tau$).
Finally, Davies and Pfenning \cite{logic-modal-staged} consider staged computations and interpret
$\square \tau$ as a type of unevaluated expressions of type $\tau$ (with no free variables).

@@

\paragraph{Thesis perspective.}
As mentioned earlier, we are interested in designing context-dependent languages and so we
use comonads for \emph{language semantics}. Uustalu and Vene present a semantics of
context-dependent computations in terms of comonads. We provide the rest of the story known
from the marriage of monads and effects. We develop coeffect calculus with an type system that
tracks the context demands more precisely (by annotating the types) and we add indexing
to comonads and link the two by giving a formal semantics. The indexing allows us to capture
applications that do not fit into the model provided by plain comonads.

@@

In the case of resources, the additional information about the context are simply added to the
variable context (as a products), but we will later look at contextual properties that affect
how variables are represented. More importantly, \emph{structural coeffects} link additional
information to individual variables in the context, rather than the context as a whole.

@@

One important note about bunched typing is that it requires a different interpretation. The omission
of weakening and contraction in linear logic means that variable can be used exactly once.
In bunched typing, variables may still be duplicated, but only using the ``;'' separator.
The type system can be interpreted as specifying whether a variable may be shared between the
body of a function and the context where a function is declared.

>>>>

Variable access represents a form of context-dependence. For example, an expression $x+y$ can be
only evaluated if the environment provides values for variables $x$ and $y$. A variable
\emph{requirement} can be satisfied in two standard ways that are characterized as \emph{dynamic}
and \emph{static} (or lexical) variable binding. Consider the following simple program:
%
\begin{equation*}
\begin{array}{l}
\kvd{let}~\ident{x}=10~\kvd{in}\\[-0.25em]
\kvd{let}~\ident{f}=\lambda \ident{y}\rightarrow \ident{x}+\ident{y}~\kvd{in}\\[-0.25em]
\kvd{let}~\ident{x}=5~\kvd{in}\\
\ident{f}~0
\end{array}
\end{equation*}
%
The program can be evaluated in two ways, depending on the variable binding mechanism:
%
\begin{itemize}
\item \textsc{Static (lexical) binding.} In a language with static binding (such as ML or Java),
  the variable \ident{x} inside the body of the lambda function is statically bound to the
  declaration in the lexical scope -- that is, the variable on the second line -- and the
  expression evaluates to 10.

\item \textsc{Dynamic binding.} In a language with dynamic binding (some variants of LISP), the
  variable value is dynamically bound to the topmost value for the available kept on the stack 
  during program execution. Thus, the \ident{x} variable inside the lambda function refers to
  \ident{x} defined on line 5 of the sample and the expression evaluates to 5.
\end{itemize}

@@

In static and dynamic scoping, all variable requirements are always placed on one site. However,
those are not the only two options. It is conceivable that a language would use a mechanism that
splits variable requirements differently and combines aspects of dynamic and static binding. For
example, the language could use static binding by default, but resort to dynamic binding if a
variable is not available in the lexical scope. One such system is implicit parameters
discussed in the next section.

Languages with static scoping resolve variable bindings at compile-time. In contrast,
languages with dynamic variable binding cannot resolve variables at compile-time. They 
typically perform runtime checks -- if a program attempts to access a variable that is not 
available in the environment, a runtime error occurs. Implementing static checking for dynamic
binding is also possible, but it requires a more sophisticated type system 
(Section~\ref{sec:path-effects-coeff}), while implementing static binding \emph{without} checking 
would be cumbersome and so dynamically scoped languages are often dynamically typed.

@@

Haskell uses static binding for ordinary variables, but GHC additionally provides a feature named
\emph{implicit parameters} \cite{app-implicit-parameters} that adds a special kind of variables,
written as \ident{?param}, which use a particular combination of static and dynamic binding.

@@

\paragraph{Thesis perspective.}
Just like the F\# function in the above example, certain expressions in context-aware languages
developed in this thesis have multiple valid typing derivations and their semantics depends on the
type. In F\#, the compiler determines a unique typing derivation based on other parts of the program
(if type is not uniquely determined, it either chooses a default or fails). In our languages, we
also determine a unique typing derivation. However, rather than relying on type information from
other parts of the program, we explicitly define an algorithm that chooses the preferred unique
derivation (Section~\ref{sec:flat-unique} and Section~\ref{sec:struct-unique}).

This approach decouples two important aspects of context-aware programming and lets us study them
independently -- the semantics of context-aware programs and the domain-specific way of resolving
ambiguities in how context demands are satisfied. In our treatment of implicit parameters, we consider
multiple typing derivations (representing a range with static and dynamic scoping at opposite ends),
but we uniquely choose one preferred typing (mimicking the behaviour of GHC for implicit parameters).

@@

Type and effect systems are usually specified as judgements of the form $\Gamma \vdash e : \tau, \cclrd{r}$,
meaning that the expression $e$ has a type $\tau$ in a (free-variable) context $\Gamma$ and
additionally may have effects described by $\cclrd{r}$. Effect systems are typically added to a
language that already supports effectful operations as a way of increasing the safety -- the type
and effect system provides stronger guarantees than a plain type system. Filinski
\cite{effects-comprehensive} refers to this approach as \emph{descriptive}\footnote{In contrast
to \emph{prescriptive} effect systems that implement computational effects in a pure language
-- such as monads in Haskell.}.

@@

When using monads, we distinguish effect-free values $\tau$ from programs, or
computations $\mtyp{}{\tau}$. The \emph{monad} $\mtyp{}{}$ abstracts the \emph{notion of
computation} and provides a way of constructing and composing effectful computations:
%
\begin{definition}
A \emph{monad} over a category $\catc$ is a triple $(M, \ident{unit}, \ident{bind})$ where:
\begin{compactitem}
\item $M$ is a mapping on objects (types) $M : \catc \rightarrow \catc$
\item $\ident{unit}$ is a mapping $\alpha \rightarrow \mtyp{}{\alpha}$
\item $\ident{bind}$ is a mapping $(\alpha \rightarrow \mtyp{}{\beta})
  \rightarrow (\mtyp{}{\alpha} \rightarrow \mtyp{}{\beta})$
\end{compactitem}
such that, for all $f:\alpha \rightarrow \mtyp{}{\beta}$ and $g:\beta \rightarrow \mtyp{}{\gamma}$:
\begin{align}
\tag{\emph{left identity}}
  \ident{bind}~\ident{unit} &= \idf{}
  \\
\tag{\emph{right identity}}
  \ident{bind}~f \circ \ident{unit} &= f
  \\
\tag{\emph{associativity}}
  \ident{bind}~(\ident{bind}~g \circ f) &= (\ident{bind}~f) \circ (\ident{bind}~g)
\end{align}
\end{definition}

\noindent
Without providing much details, we note that well known examples of monads include the partiality
monad ($\mtyp{}{\alpha} = \alpha + {\bot}$) also corresponding to the \ident{Maybe} type in
Haskell and list monad ($\mtyp{}{\tau} = 1 + (\tau \times \mtyp{}{\tau})$).
In programming language semantics, monads can be used in two distinct ways.

@@

\paragraph{Language semantics.} When using monads to provide semantics of a language, we do not
need to extend the language in any way -- we assume that the language already contains the
effectful primitives (such as the assignment operator $x \leftarrow e$). A judgement
of the form $x\!:\!\tau_1 \vdash e : \tau_2$ is interpreted as a morphism $\tau_1 \rightarrow \mtyp{}{\tau_2}$,
meaning that any expression is interpreted as an effectful computation. The semantics of variable
access and the application of a primitive function $f$ is interpreted as follows:
%
\begin{equation*}
\begin{array}{rcl}
 \sem{x\!:\!\tau_1 \vdash x : \tau_1} &=& \ident{unit}_\mtyp{}{}\\
 \sem{x\!:\!\tau_1 \vdash f~e : \tau_3} &=& (\ident{bind}_\mtyp{}{}~f) \circ \sem{e}\\
\end{array}
\end{equation*}
%
Variable access is an effect-free computation, that returns the value of the variable, wrapped
using $\ident{unit}_\mtyp{}{}$. In the second rule, we assume that $e$ is an expression using
the variable $x$ and producing a value of type $\tau_2$ and that $f$ is a (primitive) function
$\tau_2 \rightarrow \mtyp{}{\tau_3}$. The semantics lifts the function $f$ using $\ident{bind}_\mtyp{}{}$
to a function $\mtyp{}{\tau_2} \rightarrow \mtyp{}{\tau_3}$ which is compatible with the
interpretation of the expression $e$.

@@

\paragraph{Meta-language interpretation.} When designing a meta-language based on monads, we need to
extend the lambda calculus with additional type(s) and expressions that correspond to monadic
primitives:
%
\begin{align*}
\tau &:= \ident{num} \sep \tau_1 \rightarrow \tau_2 \sep \mtyp{}{\tau} \\
   e &:= x \sep f~e \sep \kvd{return}_\mtyp{}{}~e \sep \kvd{let}_\mtyp{}{}~x \Leftarrow e_1~\kvd{in}~e_2
\end{align*}
%
The types consist of the primitive type, function type and a type constructor that
represents monadic computations. Thus the expressions in the language can create both
effect-free values, such as $\tau$ and computations $\mtyp{}{\tau}$. The additional expression
$\kvd{return}_\mtyp{}{}$ is used to create a monadic computation (with no effects) from a
value and $\kvd{let}_\mtyp{}{}$ sequences effectful computations. In the semantics,
monads are not needed to interpret variable access and application, they are only used in the
semantics of additional (monadic) constructs:
%
\begin{equation*}
\begin{array}{rcl}
\sem{x\!:\!\tau \vdash x : \tau} &=& \idf{}\\
\sem{x\!:\!\tau_1 \vdash f~e : \tau_3} &=& f \circ \sem{e}\\
\sem{x\!:\!\tau_1 \vdash \kvd{return}_\mtyp{}{}~e : \mtyp{}{\tau_2}} &=& \ident{unit}_\mtyp{}{} \circ \sem{e}\\
\sem{x\!:\!\tau_1 \vdash \kvd{let}_\mtyp{}{}~y \Leftarrow e_1~\kvd{in}~e_2 : \mtyp{}{\tau_3}} &=&
  \ident{bind}_\mtyp{}{}~\sem{e_2} \circ \sem{e_1}
\end{array}
\end{equation*}

@@

While Uustalu and Vene use comonads to define the \emph{language semantics} (the first style
of Moggi), Nanevski, Pfenning and Davies use comonads as part of meta-language, in the form
of $\square$ modality, to reason about context-dependent computations (the second style of
Moggi). Before looking at the details, we use the following definition of comonad:
%
\begin{definition}
A \emph{comonad} over a category $\catc$ is a triple $(C, \ident{counit}, \ident{cobind})$ where:
\begin{compactitem}
\item $C$ is a mapping on objects (types) $C : \catc \rightarrow \catc$
\item $\ident{counit}$ is a mapping $\ctyp{}{\alpha} \rightarrow \alpha$
\item $\ident{cobind}$ is a mapping $(\ctyp{}{\alpha} \rightarrow \beta)
  \rightarrow (\ctyp{}{\alpha} \rightarrow \ctyp{}{\beta})$
\end{compactitem}
%
such that, for all $f:\ctyp{}{\alpha} \rightarrow \beta$ and $g:\ctyp{}{\beta} \rightarrow \gamma$:

@@

\noindent
The definition is dual to a monad. Intuitively, the $\ident{counit}$
operation extracts a value $\alpha$ from a value that carries additional context $\ctyp{}{\alpha}$.
The $\ident{cobind}$ operation turns a context-dependent function
$\ctyp{}{\alpha} \rightarrow \beta$ into a function that takes a value with context, applies
the context-dependent function to value(s) in the context and then propagates the context. The
next section makes this intuitive definition more concrete. More detailed discussion about
comonads can be found in Orchard's PhD thesis \cite{comonads-dom-thesis}.

@@

In the outline presented here, we ignored lambda abstraction. Similarly to monadic semantics,
where lambda abstraction requires a \emph{strong} monad, the comonadic semantics also requires
additional structure called \emph{symmetric (semi)monoidal} comonads. This structure is
responsible for the splitting of context-requirements in lambda abstraction. Note that this is
what happens in the unusual (\emph{abs}) rule in Figure~\ref{fig:path-coeff}, which distinguishes
coeffect systems from effect systems.

@@

In languages inspired by modal logics, types can have the form $\square \tau$. In the work of
Pfenning and Davies, this is the type of a term that is provable with no assumptions. In the
ML5 language by Murphy et al. \cite{app-distributed-ml5,logic-distributed-calculus}, the
$\square \tau$ type means \emph{mobile code}, that is code that can be evaluated at any node of a
distributed system (the evaluation corresponds to the axiom $\square \tau \rightarrow \tau$).
Finally, Davies and Pfenning \cite{logic-modal-staged} consider staged computations and interpret
$\square \tau$ as a type of unevaluated expressions of type $\tau$ (with no free variables).

@@

\paragraph{Thesis perspective.}
As mentioned earlier, we are interested in designing context-dependent languages and so we
use comonads for \emph{language semantics}. Uustalu and Vene present a semantics of
context-dependent computations in terms of comonads. We provide the rest of the story known
from the marriage of monads and effects. We develop coeffect calculus with a type system that
tracks the context demands more precisely (by annotating the types) and we add indexing
to comonads and link the two by giving a formal semantics. The indexing allows us to capture
applications that do not fit into the model provided by plain comonads.

@@

In the case of resources, the additional information about the context is added to the
variable context (as a product), but we will later look at contextual properties that affect
how variables are represented. More importantly, \emph{structural coeffects} link additional
information to individual variables in the context, rather than the context as a whole.

@@

One important note about bunched typing is that it requires a different interpretation. The omission
of weakening and contraction in linear logic means that variable must be used exactly once.
In bunched typing, variables may still be duplicated, but only using the ``;'' separator.
The type system can be interpreted as specifying whether a variable may be shared between the
body of a function and the context where a function is declared.
